
\documentclass[a4paper,10pt]{article}

%A Few Useful Packages
\usepackage{marvosym}
\usepackage{fontspec} 					%for loading fonts
\usepackage{xunicode,xltxtra,url,parskip} 	%other packages for formatting
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[big]{layaureo} 				%better formatting of the A4 page
% an alternative to Layaureo can be ** \usepackage{fullpage} **
\usepackage{supertabular} 				%for Grades
\usepackage{titlesec}					%custom \section

%Setup hyperref package, and colours for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

%FONTS
\defaultfontfeatures{Mapping=tex-text}
%\setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin}
%%% modified for Karol Kozioł for ShareLaTeX use
\setmainfont[
SmallCapsFont = Fontin-SmallCaps.otf,
BoldFont = Fontin-Bold.otf,
ItalicFont = Fontin-Italic.otf
]
{Fontin.otf}
%%%

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}
%Tweak a bit the top margin
%\addtolength{\voffset}{-1.3cm}

%Italian hyphenation for the word: ''corporations''
\hyphenation{im-pre-se}

%-------------WATERMARK TEST [**not part of a CV**]---------------
\usepackage[absolute]{textpos}

\setlength{\TPHorizModule}{30mm}
\setlength{\TPVertModule}{\TPHorizModule}
\textblockorigin{2mm}{0.65\paperheight}
\setlength{\parindent}{0pt}

%--------------------BEGIN DOCUMENT----------------------
\begin{document}

\pagestyle{empty} % non-numbered pages

\font\fb=''[cmr10]'' %for use with \LaTeX command

%--------------------TITLE-------------
\par{\centering
		{\Huge Mohammad Amir Jamil}
	}\bigskip\par

%--------------------SECTIONS-----------------------------------
%Section: Personal Data
\section{Personal Data}

\begin{tabular}{rl}
    \textsc{Date of Birth:} &  03-02-1993 \\
    \textsc{Address:}   & Al-Naseem, Riyadh \\
    \textsc{Phone:}     & +966-506155619\\
    \textsc{email:}     & \href{mailto:amirjamil900@gmail.com}{amirjamil900@gmail.com}\\
   \textsc{GITHUB:}    &   \href{https://github.com/amirjamil90}{github.com/amirjamil90}
\end{tabular}

%Section: Work Experience at the top
\section{Work Experience}
\begin{tabular}{r|p{11cm}}
 \textsc{OCT'17-Current} & Project Manager at \textsc{Telecommunications Consultants India Ltd}, Riyadh,Saudi Arabia \\ &\emph{Network Strategies}\\&\footnotesize{Design, Planning and Optimisation of FTTx networks.\newline
 Analysis for Optical Cost Budgeting and Preparation of Cost Estimate for various projects taking Technology Trends, Economic Stagnation as core Parameters. The Projects Include Ministry of Interior Backhaul Network, Saudi Telecom Company Managed Services for Core and Access Network.\newline 
 Coordination with Government Agencies(Ministry of Interior, Ministry of Transport, Ministry of Communication) for unhindered implementation of FTTx Deployment for clients especially Saudi Telecom Company and Dawiyat.\newline
 Developing strategies for Network Relocation for Riyadh Metro with Consortiums ANM, FAST and BACS with Optimized Network Plan.
}\\\multicolumn{2}{c}{} \\
 \textsc{Oct 2015- Oct 2017} & Project Engineer at \textsc{Telecommunications Consultants India Ltd}, Riyadh ,Saudi Arabia \\&\emph{Network Analyst}\\&\footnotesize{ Certification from Advance Level Telecom Training Center(ALTTC).\newline
 Developed Broadcast Chat Messenger for Intra-communication using Socket.io.\newline
Developed single handed Cloud Based Logistics Management System for TCIL in Saudi Arabia ,using Openshift as deployment engine and JAVA with MYSQL cartridge. Use of Poi libraries for excel files and SOLR for fast indexing.\newline
Controlled the PMCS(Project Management Control System) for TCIL in Saudi Arabia, which involves query optimization and Deviation Analysis and Milestone Completion Features.\newline
 Worked to formulate Prototype for Online Cab booking facility.... a step in e-commerce.... for 6 provinces Saudi  Arabia.}\\\multicolumn{2}{c}{} \\
\textsc{Jun 2015 - Oct 2015} & Software Development Engineer at \textsc{Jabong}, \newline \emph{Developer}\\&\footnotesize{Handled the Cancel Order page UI and Front End in Sails.js.Developed services, controller and policies for the feature.\newline
Implemented the Test Driven Development for the module with Mocha and Chai.\newline
Optimisation of Jabong Search Suggestion which included POC for individual time break up for the modules. Made use of
concurrent request tool handler (siege) for latency. Meanwhile developed Locust module to do the same.\newline
Made a JavaScript Error Logging Module which would log errors of the frontend in chronologic order.\newline
Developed a Bunyan logger for the Bussiness Logic Layer of Jabong.\newline
Made a Nightwatch module for automated testing for complete catalogue testing.\newline}
\end{tabular}
%Section: Education
\section{Education}
\begin{tabular}{rl}
 \textsc{2011-2015} & B.Tech Computer Engineering  from Jamia Millia Islamia, New-Delhi. 9.08/10 \normalsize\\
\textsc{2010-2011} &Intermediate from City Montessori School.  92.5\% \normalsize\\
\textsc{2008-2009} & HighSchool from City Montessori School.  92\% \normalsize\\
\end{tabular}

%Section: Research
\section{Researches}
\textbf{Digital Image Authentication And Encryption Using Digital Signature:} \normalsize Image Encryption using Reed Solomon
Encoding and Digital Signature(hash function and RSA)with Logistic Map chaotic shuffling. \textbf{The research has been accepted and given ‘BEST PAPER AWARD’ by IEEE.} \\
\textbf{Image Steganography using Genetic Algorithm and Visual Cryptography: } \normalsize Digital Image Encryption Using Matrix
Crossover Technique of Genetic Algorithm. Splitting of image in n-shares using Visual Cryptography. \\
\textbf{Certified by University of Toronto for online course “Learn To Program The Fundamentals”.}

%Section: Communications
\section{Communication}
\textsc{Mar'15: }\textbf{IEEE Conference, Ghaziabad.} \normalsize 
Presented Reaseach Paper titled "Digital Image Authentication and Encryption Using Digital Signature". \\
\textsc{Sept'15: }\textbf{Algorithmic Session,Jabong.} \normalsize
Delivered a talk on Run Time Complexity and Optimization of API calls for the Front-End Team of Jabong. \\
\textsc{May'17: }\textbf{Innovative Ideas for Telecommunication Networks for National BroadBand Plan 2020, Saudi Arabia.} Delivered a Presentation for Innovative Ideas to Saudi Telecom Company for National Broadband Plan 2020.The talk focused on cost Optimization, Shifting to Mobile Platform and Network Planning. \\
\textsc{Sept'17: }\textbf{Presentation on Cloud Services for Call Center to MoCIT,Riyadh.} The Presentation was Technical Proposal for setting up Call Centre for Saudi Arabia focusing on Cloud Data Storage and Big Data Processing using Hadoop.\\
\normalsize

%Section: Projects
\section{Projects}
\textbf{Generic Base Calculator:} \normalsize Java Based Application to perform Binary Operations upto Base 40. \\
\textbf{Hostel Management Project:} \normalsize A web based project for hostel management using Jsp and MYSQL database. \\
\textbf{Snap And Shop:} \normalsize Android application for customer support on e-commerce websites. This application is for image search on e-commerce websites which uses fuzzy logic approach and tags search for specific product and gives the best price list i.e A comparator for different e-commerce websites. \\
\textbf{Ball above the bar:} \normalsize A d-x ball like game using Scratch during online course CS-50 by Harvard Universty.\\
\textbf{All Servers on Single Click:} \normalsize It’s a Swing application that I built for launching different Servers like Wamp,Weblogic, Xamp from a single click which ease my work during Development.
\textbf{Scripts \& Tools :} \normalsize Have written JS scripts to ease my web work and configured AutohotKey for working in Windows.\\
\textbf{Locat :} \normalsize My recent project is to expand the concept of Location Identifier. Using Semantic Analysis to query Address and get back the Coordinates of Queried Sentence. Working to optimise the Algorithm for accurate results. 


\section{Technical Skills and Interests}
\textbf{Programming Languages:} C, C++, JAVA, Python, Haskell. \\
\textbf{Web:} HTML, JavaScript, Node.\\
\textbf{Frameworks:} Sails.js, Spring, Hibernate, DUST, Nightwatch.\\
\textbf{Operating System:} Windows, Linux(Debian).\\
\textbf{Interests:} Oratory, Driving, Table Tennis, Music,Casio Playing.\\
\end{document}
